```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 

```{r}
install.packages('ggrepel')

library(ggplot2)
library(tidyverse)
library(ggrepel)
```

```{r}
kib <- readxl::read_xlsx('KIB - Best in Show (public).xlsx', sheet='Best in show full sheet')
names(kib) <- kib[2, ]
kib <- kib[4:nrow(kib), which(names(kib) %in% c('Sources - see bottom right', 'category', 'ULTIMATE TOP DOG MEGA SCORE', 'POPULAR RATING', 'size category', 'intelligence category'))]
names(kib) <- c('Breed', 'Category', 'Score', 'Popularity', 'Size', 'Intelligence')
kib <- kib %>% drop_na()
kib$Score <- as.numeric(kib$Score) 
kib$Popularity <- as.numeric(kib$Popularity)

kib$Score <- kib$Score / 4.5 * 100
kib$Popularity <- kib$Popularity / max(kib$Popularity) * 100

kib$Intelligence <- ifelse(kib$Intelligence %in% c('Brightest', 'Excellent', 'Above average', 'Clever'), 'Clever', 'Dumb')

kib$Intelligence <- factor(kib$Intelligence, levels = c('Dumb', 'Clever'))

kib %>%
  ggplot(aes(x = Score, y = -Popularity, color = Category, shape = Size, size = Intelligence)) +
  geom_vline(xintercept = 50) +
  geom_hline(yintercept = -50) +
  geom_jitter() +
  geom_point() +
  geom_text_repel(aes(label = Breed, size = 'Dumb')) +
  xlab('Data Score') + ylab('Popularity') + ggtitle('The Ultimate Data Dog')
  theme(axis.text.x = element_text(size = 0), axis.text.y = element_text(size = 0))
```
